### 2020-07-14 CILAMCE_2020/paper.tex
Update table and figure to uppercase

% --------------------------------------------------------------------------
\section{Results}\label{sec:Results}
% --------------------------------------------------------------------------
The test RMSE for each model in ascending order of age was 3.31, 4.36, 4.62, 4.72, 5.94 and 5.85 respectively. The table \ref{tab:results} presents the details and results of each model, including the naive one. The figure \ref{fig:results} compares the actual and predicted values for the final models.

@@

The models built present satisfactory results and prove that the compressive strength of concrete can be predicted relatively easily.The alternative adopted to create a model for each set of age proved to be a valid method, instead of using the age as a predictor along with the ingredients like all studies cited in the introduction with the same dataset. This stratification managed to obtain different results for each age group. Although the RMSE of these studies and the found here were close. The table \ref{tab:comparison} shows the comparison between these studies and the 28 days model developed here.

>>>>

% --------------------------------------------------------------------------
\section{Results}\label{sec:Results}
% --------------------------------------------------------------------------
The test RMSE for each model in ascending order of age was 3.31, 4.36, 4.62, 4.72, 5.94 and 5.85 respectively. The Table \ref{tab:results} presents the details and results of each model, including the naive one. The Fig. \ref{fig:results} compares the actual and predicted values for the final models.

@@

The models built present satisfactory results and prove that the compressive strength of concrete can be predicted relatively easily.The alternative adopted to create a model for each set of age proved to be a valid method, instead of using the age as a predictor along with the ingredients like all studies cited in the introduction with the same dataset. This stratification managed to obtain different results for each age group. Although the RMSE of these studies and the found here were close. The Table \ref{tab:comparison} shows the comparison between these studies and the 28 days model developed here.
